---
title: "Case Study 1"
author: "Rose Killian"
output: github_document
---

### Loading libraries and data

```{r}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

library(p8105.datasets)

```


## Load a data set

```{r}
data(nyc_airbnb)
```

*How many rentals are there? Of what type? In what places?
*Is price correlated with review score?
*Which neighborhood is most popular? Most expensive?
*Which neighborhood has the highest reviews?
*Is availability related to price?
Is room type related to neighborhood?
*Is length of stay related to neighborhood group?


```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(borough = neighbourhood_group)
```

so let's count things

```{r}
nyc_airbnb %>% 
  janitor::tabyl(borough, room_type)
```


```{r}
nyc_airbnb %>% 
  count(borough, room_type)
  
```

```{r}
range(pull(nyc_airbnb, stars), na.rm = T)

nyc_airbnb %>% 
  filter(stars == 1)
```

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = price, y = stars, color = borough)) +
  geom_point()


nyc_airbnb %>% 
  filter(price < 2500) %>% 
  ggplot(aes(x = price, y = stars, color = borough)) +
  geom_point()


nyc_airbnb %>% 
  filter(price < 2500) %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
```

Looking at price and room type:

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point() +
  facet_grid(. ~ room_type)
```

Price and neighborhood
```{r}
nyc_airbnb %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = T)) %>% 
  arrange(mean_price)

nyc_airbnb %>% 
  filter(borough == "Manhattan", price <= 1000) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip() +
    facet_grid(. ~ room_type)
```

Price vs Location

```{r}
nyc_airbnb %>%
  sample_n(5000) %>% 
  filter(price < 500) %>% 
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = .5)
```

## retry leaflet

```{r, eval = F}
library(leaflet)

nyc_airbnb %>% 
  sample_n(5000) %>% 
  filter(price < 500) %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(~lat, ~long)

nyc_airbnb %>% 
  sample_n(5000) %>% 
  filter(price < 500) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 1)

pal = colorNumeric("viridis", NULL)

nyc_airbnb %>% 
  filter(price < 500) %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 1, color =  ~pal(stars))
```



